The formal verification of the ctm approach to forcing \thanks{Supported by Secyt-UNC projects 33620180100855CB and 33620180100465CB, and Conicet.}

### 2023-09-27 Independence_CH/axioms_metatheory.tex
Explanation of Hessenberg and minor edits

\subsection{IFOL and FOL}
In the axioms \isa{refl}, \isa{subst}, \isa{allI}, \isa{spec},
\isa{exE}, \isa{exI}, and \isa{eq\_reflection} there is a constraint
for the \emph{type of} the variables \isa{a, b, x} to be in the class \isa{term\_class}.
\begin{isabelle}
IFOL.FalseE: ⋀P. False ⟹ P\isanewline
IFOL.refl:  (⋀a. a = a)\isanewline
IFOL.subst: (⋀a b P. a = b ⟹ P(a) ⟹ P(b))\isanewline
IFOL.allI:  (⋀P. (⋀x. P(x)) ⟹ ∀x. P(x))\isanewline
IFOL.spec:  (⋀P x. ∀x. P(x) ⟹ P(x))\isanewline
IFOL.exE:   (⋀P R. ∃x. P(x) ⟹ (⋀x. P(x) ⟹ R) ⟹ R)\isanewline
IFOL.exI:   (⋀P x. P(x) ⟹ ∃x. P(x))\isanewline
IFOL.conjI: ⋀P Q. P ⟹ Q ⟹ P ∧ Q\isanewline
IFOL.conjunct1: ⋀P Q. P ∧ Q ⟹ P\isanewline
IFOL.conjunct2: ⋀P Q. P ∧ Q ⟹ Q\isanewline
IFOL.disjE: ⋀P Q R. P ∨ Q ⟹ (P ⟹ R) ⟹ (Q ⟹ R) ⟹ R\isanewline
IFOL.disjI1: ⋀P Q. P ⟹ P ∨ Q\isanewline
IFOL.disjI2: ⋀P Q. Q ⟹ P ∨ Q\isanewline
IFOL.eq\_reflection: (⋀x y. x = y ⟹ x ≡ y)\isanewline
IFOL.iff\_reflection: ⋀P Q. P ⟷ Q ⟹ P ≡ Q\isanewline
IFOL.impI: ⋀P Q. (P ⟹ Q) ⟹ P ⟶ Q\isanewline
IFOL.mp: ⋀P Q. P ⟶ Q ⟹ P ⟹ Q\isanewline%\isanewline
FOL.classical: ⋀P. (¬ P ⟹ P) ⟹ P
\end{isabelle}

>>>>

\subsection{IFOL and FOL}
In the axioms \isa{refl}, \isa{subst}, \isa{allI}, \isa{spec},
\isa{exE}, \isa{exI}, and \isa{eq\_reflection} there is a constraint
for the \emph{type} of the variables \isa{a, b, x} to be in the class \isa{term\_class}.
\begin{isabelle}
IFOL.FalseE: ⋀P. False ⟹ P\isanewline
IFOL.refl:  (⋀a. a = a)\isanewline
IFOL.subst: (⋀a b P. a = b ⟹ P(a) ⟹ P(b))\isanewline
IFOL.allI:  (⋀P. (⋀x. P(x)) ⟹ ∀x. P(x))\isanewline
IFOL.spec:  (⋀P x. ∀x. P(x) ⟹ P(x))\isanewline
IFOL.exE:   (⋀P R. ∃x. P(x) ⟹ (⋀x. P(x) ⟹ R) ⟹ R)\isanewline
IFOL.exI:   (⋀P x. P(x) ⟹ ∃x. P(x))\isanewline
IFOL.conjI: ⋀P Q. P ⟹ Q ⟹ P ∧ Q\isanewline
IFOL.conjunct1: ⋀P Q. P ∧ Q ⟹ P\isanewline
IFOL.conjunct2: ⋀P Q. P ∧ Q ⟹ Q\isanewline
IFOL.disjE: ⋀P Q R. P ∨ Q ⟹ (P ⟹ R) ⟹ (Q ⟹ R) ⟹ R\isanewline
IFOL.disjI1: ⋀P Q. P ⟹ P ∨ Q\isanewline
IFOL.disjI2: ⋀P Q. Q ⟹ P ∨ Q\isanewline
IFOL.eq\_reflection: (⋀x y. x = y ⟹ x ≡ y)\isanewline
IFOL.iff\_reflection: ⋀P Q. P ⟷ Q ⟹ P ≡ Q\isanewline
IFOL.impI: ⋀P Q. (P ⟹ Q) ⟹ P ⟶ Q\isanewline
IFOL.mp: ⋀P Q. P ⟶ Q ⟹ P ⟹ Q\isanewline%\isanewline
FOL.classical: ⋀P. (¬ P ⟹ P) ⟹ P
\end{isabelle}
